Topology and experimental distinguishability

### 2017-07-18 Articles/TopologyAndExperimentalDistinguishability/article.tex
wrote out some of the old definitions in a more mathematical way

\begin{defn}
	A \emph{statement} $\mathsf{s}$ is a declarative sentence that is either true or false, as in classical logic. Here, we allow for infinite statements. 
\end{defn}

In addition to the usual logical operations on statements, we introduce the following notation:

\begin{defn}
We say two statements $s$ and $t$ are \emph{compatible}, denoted $s\comp t$, if the conjunction $s\wedge t$ is not a contradiction; otherwise they are \emph{incompatible}, denoted $s\ncomp t$. 
\end{defn}

@@

\begin{defn}
	An \emph{experimental test} $\mathsf{e}$ is a repeatable procedure (i.e. it can be restarted and stopped an arbitrary number of times) that, if successful, terminates in a finite amount of time.
\end{defn}

\begin{defn}
	An \emph{experimental observation} is a tuple $\mathsf{o} = \llparenthesis \mathsf{s}, \mathsf{e} \rrparenthesis$ composed by a statement $\mathsf{s}$ and an experimental test $\mathsf{e}$ such that the statement is true if and only if the  experimental test is always successful. The experimental observation is \emph{verified} if the statement is true.
\end{defn}

\begin{defn}
	An \emph{experimental counter-observation} is a tuple $\mathsf{o}^c= \llbracket \mathsf{s}, \mathsf{e} \rrbracket$ composed by a statement $\mathsf{s}$ and an experimental test $\mathsf{e}$ such that the statement is false if and only if the experimental test is always successful. The experimental counter-observation is \emph{refuted} if the statement is false.
\end{defn}

@@

\begin{defn}
	Given two experimental observations $\mathsf{o}_1$ and $\mathsf{o}_2$ we define:
	\begin{itemize}
	\item \emph{implication}: $\mathsf{o}_1 \imp \mathsf{o}_2$ ($\mathsf{o}_1$ implies $\mathsf{o}_2$) if $\mathsf{o}_2$ is always verified whenever $\mathsf{o}_1$ is verified
	\item \emph{equivalence}: $\mathsf{o}_1 = \mathsf{o}_2$ ($\mathsf{o}_1$ is equal to $\mathsf{o}_2$) if $\mathsf{o}_1 \imp \mathsf{o}_2$ and $\mathsf{o}_2 \imp \mathsf{o}_1$
	\item \emph{compatibility}: $\mathsf{o}_1 \comp \mathsf{o}_2$ ($\mathsf{o}_1$ is compatible with $\mathsf{o}_2$) if there exists a case in which $\mathsf{o}_1$ and $\mathsf{o}_2$ are jointly verified
	\end{itemize}
    The negation of these properties will be noted by $\nimp$, $\neq$ , $\ncomp$ respectively.
\end{defn}

@@

\begin{defn}
	The \emph{null observation} is any experimental observation that is never verified (i.e. the experimental test will never terminate successfully). 
\end{defn}

@@

\begin{defn}
	The \emph{negation} or \emph{logical NOT} of an experimental observation $\mathsf{o}=\llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ is the experimental counter-observation $\neg \mathsf{o}=\llbracket\neg \mathsf{s}, \mathsf{e}\rrbracket$ where the negation of the statement $\mathsf{s}$ can be refuted by the experimental test $\mathsf{e}$.
\end{defn}

@@

\begin{defn}
	The \emph{conjunction} or \emph{logical AND} of a finite collection  of experimental observations $\{\mathsf{o}_i\}_{i=1}^{n}=\{\llparenthesis \mathsf{s}_i, \mathsf{e}_i\rrparenthesis\}_{i=1}^{n}$ is the experimental observation $\bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ where $\mathsf{s} = \bigwedge\limits_{i=1}^{n} \mathsf{s}_i$ is the conjunction of the respective statements and $\mathsf{e} = \mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ is the experimental test that successfully terminates if and only if all $\{\mathsf{e}_i\}_{i=1}^{n}$ successfully terminate.
\end{defn}

@@

\begin{defn}
	The \emph{disjunction} or \emph{logical OR} of a countable (finite or infinite) collection of experimental observations $\{\mathsf{o}_i\}_{i=1}^{\infty}=\{\llparenthesis \mathsf{s}_i, \mathsf{e}_i\rrparenthesis\}_{i=1}^{\infty}$ is the experimental observation $\bigvee\limits_{i=1}^{\infty} \mathsf{o}_i = \llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ where $\mathsf{s} = \bigvee\limits_{i=1}^{\infty} \mathsf{s}_i$ is the disjunction of the respective statements and $\mathsf{e} = \mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ is the experimental test that successfully terminates if and only if at least one experimental test in $\{\mathsf{e}_i\}_{i=1}^{\infty}$ successfully terminates.
\end{defn}

@@

@@

\begin{defn}
	An \emph{experimental domain} is a set of observations closed under finite conjunction and countable disjunction such that all observations can be tested in infinite time. 
\end{defn}

\begin{defn}
	A \emph{sub-basis} of an experimental domain is any subset that can generate all others via finite conjunction and countable disjunction. A \emph{basis} of an experimental domain is any subset that can generate all others by countable disjunctions. 
\end{defn}

@@

\begin{rem} 
It is not hard to see that the (countable) disjunction of an entire basis produces an experimental observation which is always verified. Henceforth, we call this the \emph{trivial observation}. 
\end{rem}

@@

We will now use our notions of experimental observations and experimental domains to construct a new space with a topology which will more rigorously capture our notion of ``exact" possibilities. We will begin with a given experimental domain $\mathcal{S}$. First, we will construct an intermediate space which will mimic the Borel algebra of a topological space:

\begin{defn}
Given an experimental domain $\mathcal{S}$, define the associated \emph{theoretical domain} $\mathcal{S}^*$ to be the closure under countable conjunction, disjunction, and negation of the set of statements in all experimental observations of $\mathcal{S}$.
\end{defn}

Next, we will extract the appropriate subcollection of the theoretical domain in order to obtain what will serve as ``points" in our space:

\begin{defn}
\label{possibilitiesdef}
Given a theoretical domain $\mathcal{S}^*$, define the set $X$ of \emph{possibilities} to be the following subset:
$$
X = \{s\in\mathcal{S}^*\ |\ \forall t\in\mathcal{S}^*, \text{ either } s\imp t \text{ or } s\ncomp t\}
$$
\end{defn}

Of course, the nature of the set $X$ will vary greatly depending on the behavior of the collection $\mathcal{S}$ of observations. The following function will provide us with a collection of distinguished subsets of $X$. Define the \emph{verification function} $U:\mathcal{S}\to 2^X$, the set of subsets of $X$, by:
$$
U(\mathsf{o}) = \{s\in X\ |\ \mathsf{o}\text{ is successful if }s\text{ is true}\}.
$$
This function behaves nicely with our algebra of observations:
\begin{lem}
\label{ubehavior}
Let $\mathsf{o}_1,\mathsf{o}_2,\ldots$ be some collection of observations. Then we have:
$$U(\bigwedge\limits_{i=1}^{n} \mathsf{o}_i) = \bigcap\limits_{i=1}^{n} U (\mathsf{o}_i) \text{ and }U(\bigvee\limits_{i=1}^{\infty} \mathsf{o}_i) = \bigcup\limits_{i=1}^{\infty} U (\mathsf{o}_i).$$
That is, $U$ respects finite conjunction and countable disjunction.
\end{lem}
\begin{proof}
Notice that $s\in U(\bigwedge\limits_{i=1}^{n} \mathsf{o}_i)$ if and only if all of the $\mathsf{o}_i$ are successful whenever $s$ is true. This is equivalent to the right-hand side, i.e. $s\in \bigcap\limits_{i=1}^{n} U (\mathsf{o}_i)$. The other equality is similarly straightforward. 
\end{proof}

\begin{thm}
For an experimental domain $\mathcal{S}$ with set of possibilities $X$ and verification function $U$, the collection $\mathsf{T} = U(\mathcal{S})\subset2^X$ is a Hausdorff, second-countable topology on $X$.
\end{thm}
\begin{proof}
First, the null obervation will map to the empty set, and the trivial observation will map to all of $X$. Next, we must check arbitrary union and finite intersections. Recall that the experimental domain $\mathcal{S}$ has a countable basis $\mathcal{B} = \{\mathsf{o}_1,\mathsf{o}_2,\ldots\}$.

Let $\{U_i\ |\ i\in I\}\subseteq \mathsf{T}$, where $I$ is some indexing set. Let $U_i = U(\mathsf{O}_i)$, where each $\mathsf{O}_i = \bigcup\limits_{j=1}^{\infty}\mathsf{o}_{n_{i,j}}$ for appropriately indexed basis elements $\mathsf{o}_{n_{i,j}}$, where $n_{i,j}$ is a positive integer. Now, since there are only countably many basis elements, we know that there are only countably many distinct $n_{i,j}$'s, so we may define a sequence of positive integers $m_k, k=1,2,\ldots$ such that $$\{m_k\}_{k=1}^{\infty} = \{n_{i,j}\ |\ i\in I, j=1,2,\ldots\}.$$ Then using Lemma \ref{ubehavior}, we have the following:
$$
\bigcup\limits_{i\in I}U(\mathsf{O}_i) = \bigcup\limits_{i\in I}\bigcup\limits_{j=1}^{\infty}U(\mathsf{o}_{n_{i,j}}) = \bigcup\limits_{k=1}^{\infty}U(\mathsf{o}_{m_k}) = U(\bigvee\limits_{k=1}^{\infty} \mathsf{o}_{m_k})
$$
which is an element of $\mathsf{T}$, so this collection is closed under arbitrary union.

The proof for finite intersection is simpler. Let $\{U_i\}_{i=1}^N$ be a finite collection of elements of $\mathsf{T}$. Then as above writing $U_i = U(\mathsf{O}_i)$, we have:
$$
\bigcap\limits_{i=1}^N U(\mathsf{O}_i) = U(\bigwedge\limits_{i=1}^{N} \mathsf{O}_i)
$$
by Lemma \ref{ubehavior}, as required. Hence $\mathsf{T}$ is a topology. In what follows we will refer to elements of $\mathsf{T}$ as open sets.

It is immediate that this topology is second-countable, since by Lemma \ref{ubehavior} the countable basis of observations for $\mathcal{S}$ becomes under $U$ a countable basis for the topology $\mathsf{T}$. To see why it is Hausdorff, let $x,y\in X$ be distinct possibilities. From Definition \ref{possibilitiesdef}, we have several cases to consider; however, it turns out that only one is possible. Without loss of generality, suppose $x\imp y$. But then we have $x\comp y$, so by symmetry we must also have $y\imp x$; in other words, $x=y$, contrary to assumption. It follows that $x\ncomp y$. Now suppose for a contradiction that for every open set $U\ni x$ and $V\ni y$ we have $U\cap V\neq \emptyset$. TODO: PROBLEM

\end{proof}

\begin{prop}
	A Hausdorff and second countable space $X$ has at most cardinality of continuum.
\end{prop}

@@

This means that, no matter what technique we use now or in the future, the collections of elements that we can properly define experimentally are at most infinite like the continuum. This already gives us a first simple and basic requirement a set of mathematical objects need to pass to be of scientific interest.

@@

\section{Example of an Experimental Domain}

Consider the collection of statements, ``this object has a mass strictly between $x$ and $y$ kilograms" where $x$ and $y$ are any positive real numbers with $x<y$. Consider the experimental test where we put the object on a balance with an appropriate level of precision for each corresponding statement. Then each observation may be equated to an open interval of positive real numbers $(x,y)\subset\mathbb{R}$. Conjunction and disjunction of these observations will correspond exactly to intersection and union of these intervals, respectively. Further, the collection of intervals of the form $(p,q)$ for $p,q\in\mathbb{Q}$ forms a basis of observations. Next, one can show that any sequence of observations satisfying the conditions of exact outcome corresponds precisely to a real number. In particular, the set of possibilities $X$ for this experimental domain will be the set of positive real numbers with their usual topology. The reader with some experience with elementary real analysis will recognize that this construction is essentially the same as the Cauchy sequence construction of the real numbers, where representative Cauchy sequences come from endpoints of intervals, and the intervals used those corresponding to observations in a sequence of observations yielding an exact outcome.

@@

Now that we have defined the possibilities of our domains and the topology associated with them, we want to establish relationships between them. We want to do this because the aim of scientific investigation is studying and characterizing these relationships

@@

TODO: add corollary environment for this one.

\begin{prop}
The topology $\mathsf{T}(\mathcal{C})$ on the set of continuous functions $C(\mathbb{R},\mathbb{R})$ from $\mathbb{R}$ to itself is in general not equal to the open-open topology on $C(\mathbb{R},\mathbb{R})$.
\end{prop}
\begin{proof}
In the proof of the previous proposition, note that the basis for the open-open topology is independent of the basis used for the underlying spaces, and in particular is a superset of the basis for $\mathsf{T}(\mathcal{C})$ when using $\mathbb{B}_2$ to construct it. Hence the open-open topology is distinct from $\mathsf{T}(\mathcal{C})$ when using the basis $\mathcal{B}_1$ on $\mathbb{R}$. 
\end{proof}

@@

\section*{Acknowledgments}
Funding for this work was provided in part by the MCubed program of the University of Michigan.

>>>>

\begin{defn}
	A \textbf{statement} $\mathsf{s}$ is a declarative sentence that is either true or false, as in classical logic. 
\end{defn}

@@

\begin{defn}
	An \textbf{experimental test} $\mathsf{e}$ is a repeatable procedure (i.e. it can be restarted and stopped an arbitrary number of times) that, if successful, terminates in a finite amount of time.
\end{defn}

\begin{defn}
	An \textbf{experimental observation} is a tuple $\mathsf{o} = \llparenthesis \mathsf{s}, \mathsf{e} \rrparenthesis$ composed by a statement $\mathsf{s}$ and an experimental test $\mathsf{e}$ such that the statement is true if and only if the  experimental test is always successful. The experimental observation is \textbf{verified} if the statement is true.
\end{defn}

\begin{defn}
	An \textbf{experimental counter-observation} is a tuple $\mathsf{o}^c= \llbracket \mathsf{s}, \mathsf{e} \rrbracket$ composed by a statement $\mathsf{s}$ and an experimental test $\mathsf{e}$ such that the statement is false if and only if the experimental test is always successful. The experimental counter-observation is \textbf{refuted} if the statement is false.
\end{defn}

@@

\begin{defn}
	Given two experimental observations $\mathsf{o}_1$ and $\mathsf{o}_2$ we define:
	\begin{itemize}
	\item \textbf{implication}: $\mathsf{o}_1 \imp \mathsf{o}_2$ ($\mathsf{o}_1$ implies $\mathsf{o}_2$) if $\mathsf{o}_2$ is always verified whenever $\mathsf{o}_1$ is verified
	\item \textbf{equivalence}: $\mathsf{o}_1 = \mathsf{o}_2$ ($\mathsf{o}_1$ is equal to $\mathsf{o}_2$) if $\mathsf{o}_1 \imp \mathsf{o}_2$ and $\mathsf{o}_2 \imp \mathsf{o}_1$
	\item \textbf{compatibility}: $\mathsf{o}_1 \comp \mathsf{o}_2$ ($\mathsf{o}_1$ is compatible with $\mathsf{o}_2$) if there exists a case in which $\mathsf{o}_1$ and $\mathsf{o}_2$ are jointly verified
	\end{itemize}
    The negation of these properties will be noted by $\nimp$, $\neq$ , $\ncomp$ respectively.
\end{defn}

@@

\begin{defn}
The \textbf{null observation}, denoted $\mathsf{o}_N$, is any experimental observation that is never verified (i.e. the experimental test will never terminate successfully).
\end{defn}

@@

\begin{defn}
	The \textbf{negation} or \textbf{logical NOT} of an experimental observation $\mathsf{o}=\llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ is the experimental counter-observation $\neg \mathsf{o}=\llbracket\neg \mathsf{s}, \mathsf{e}\rrbracket$ where the negation of the statement $\mathsf{s}$ can be refuted by the experimental test $\mathsf{e}$.
\end{defn}

@@

\begin{defn}
	The \textbf{conjunction} or \textbf{logical AND} of a finite collection  of experimental observations $\{\mathsf{o}_i\}_{i=1}^{n}=\{\llparenthesis \mathsf{s}_i, \mathsf{e}_i\rrparenthesis\}_{i=1}^{n}$ is the experimental observation $\bigwedge\limits_{i=1}^{n} \mathsf{o}_i = \llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ where $\mathsf{s} = \bigwedge\limits_{i=1}^{n} \mathsf{s}_i$ is the conjunction of the respective statements and $\mathsf{e} = \mathsf{e}_\wedge(\{\mathsf{e}_i\}_{i=1}^{n})$ is the experimental test that successfully terminates if and only if all $\{\mathsf{e}_i\}_{i=1}^{n}$ successfully terminate.
\end{defn}

@@

\begin{defn}
	The \textbf{disjunction} or \textbf{logical OR} of a countable (finite or infinite) collection of experimental observations $\{\mathsf{o}_i\}_{i=1}^{\infty}=\{\llparenthesis \mathsf{s}_i, \mathsf{e}_i\rrparenthesis\}_{i=1}^{\infty}$ is the experimental observation $\bigvee\limits_{i=1}^{\infty} \mathsf{o}_i = \llparenthesis \mathsf{s}, \mathsf{e}\rrparenthesis$ where $\mathsf{s} = \bigvee\limits_{i=1}^{\infty} \mathsf{s}_i$ is the disjunction of the respective statements and $\mathsf{e} = \mathsf{e}_\vee(\{\mathsf{e}_i\}_{i=1}^{\infty})$ is the experimental test that successfully terminates if and only if at least one experimental test in $\{\mathsf{e}_i\}_{i=1}^{\infty}$ successfully terminates.
\end{defn}

@@

\begin{rem}
A useful equivalent characterization of $\mathsf{o}\imp\mathsf{o}'$ for observations $\mathsf{o}$ and $\mathsf{o}'$ is provided by the above constructions. We note that $\mathsf{o}\imp\mathsf{o}'$ if and only if $\mathsf{o}\wedge\mathsf{o}' = \mathsf{o}'$ if and only if $\mathsf{o}\vee\mathsf{o}'=\mathsf{o}$. 
\end{rem}

@@

\begin{defn}
	An \textbf{experimental domain} is a set of observations closed under finite conjunction and countable disjunction such that all observations can be tested in infinite time. 
\end{defn}

\begin{defn}
	A \textbf{sub-basis} of an experimental domain is any subset that can generate all others via finite conjunction and countable disjunction. A \textbf{basis} of an experimental domain is any subset that can generate all others by countable disjunctions. 
\end{defn}

@@

\begin{rem}
It is not hard to see that the (countable) disjunction of an entire basis produces an experimental observation which is always verified. Henceforth, we call this the \textbf{trivial observation}, denoted $\mathsf{o}_T$.
\end{rem}

@@

\begin{defn}
A \textbf{set of possibilities} $(X,x^*)$ is a set together with a distinguished element $x^*$. 
\end{defn}

\begin{defn}
	A \textbf{verifiable set} $U \subseteq X$ is a subset of possibilities for which there exists an experimental observation $\mathsf{o} = (x^*\in U, \mathsf{e}_\in(U))$ where $\mathsf{e}_\in(U)$ is an experimental test that succeeds only if the object to identify is an element of $U$.
\end{defn}

\begin{defn}
	A \textbf{refutable set} $U \subseteq X$ is a subset of possibilities for which there exists an experimental counter-observation $\mathsf{o} = (x^*\in U, \mathsf{e}_{\notin}(U))$ where $\mathsf{e}_{\notin}(U)$ is an experimental test that succeeds only if the object to identify is not an element of $U$.
\end{defn}

\begin{lem}
\label{complements}
	The complement $U^C$ of a verifiable set $U \subseteq X$ is a refutable set.
\end{lem}

\begin{proof}
	Let $U\subset X$ be a verifiable set. There exists an experimental observation $\mathsf{o} = (x^*\in U, \mathsf{e}_\in(U))$. Consider $\neg \mathsf{o} = (\neg x^*\in U, \mathsf{e}_\in(U)) = (x^*\notin U, \mathsf{e}_{\notin}(U^C)) = (x^*\in U^C, \mathsf{e}_{\notin}(U^C))$. That is, there exists a counter-observation $(x^*\in U^C, \mathsf{e}_{\notin}(U^C))$. Therefore $U^C$ is a refutable set.
\end{proof}

\begin{lem}
\label{setbehavior}
	Let $U_1, U_2, ... , U_n, ...$ be a countable infinite sequence of verifiable sets. The finite intersection $\bigcap\limits_{i=1}^{n} U_i$ and the countable union $\bigcup\limits_{i=1}^{\infty} U_i$ are verifiable sets.
\end{lem}

\begin{proof}
	We claim the finite intersection of verifiable sets is a verifiable set. Let $U_1, U_2, ... , U_n \subseteq X$ be n verifiable sets. For each $U_i$ there exists an experimental observation $\mathsf{o}_i = (x^*\in U_i, \mathsf{e}_\in(U_i))$. Consider $\mathsf{o} = \bigwedge\limits_{i=1}^{n} \mathsf{o}_i = (\bigwedge\limits_{i=1}^{n} x^*\in U_i , \mathsf{e}_{\wedge}(\mathsf{e}_\in(U_i)))=( x^*\in \bigcap\limits_{i=1}^{n} U_i, \mathsf{e}_\in(\bigcap\limits_{i=1}^{n} U_i))$ is an experimental observation. We conclude $\bigcap\limits_{i=1}^{n} U_i$ is a verifiable set.

	We claim the countable union of verifiable sets is a verifiable set. Let $U_1, U_2, ... , U_n, ... \subseteq X$ be an infinite sequence of verifiable sets. For each $U_i$ there exists an experimental observation $\mathsf{o}_i = (x^*\in U_i, \mathsf{e}_\in(U_i))$. Consider $\mathsf{o} = \bigvee\limits_{i=1}^{\infty} \mathsf{o}_i = (\bigvee\limits_{i=1}^{\infty} x^*\in U_i, \mathsf{e}_{\vee}(\mathsf{e}_\in(U_i)))=( x^*\in \bigcup\limits_{i=1}^{\infty} U_i, \mathsf{e}_\in(\bigcup\limits_{i=1}^{\infty} U_i))$ is an experimental observation. Thus $\bigcup\limits_{i=1}^{\infty} U_i$ is a verifiable set.
\end{proof}

Next, we wish to isolate the possibility spaces for which there exists an appropriate collection of experimental observations. Let $(X,x^*)$ be a set of experimental possibilities. An \textbf{experimental identification} is any experimental observation of the form $(x^*\in S,\mathsf{e}_{\in}(S))$, where $S$ is any subset of $X$.

\begin{defn}
	A set of experimental possibilities $X$ is \textbf{experimentally distinguishable} if there exists a collection $\mathsf{T}$ of experimental identifications which form an experimental domain such that given any two possibilities $x_1, x_2 \in X$ we can always find two mutually exclusive experimental observation such that each possibility is compatible with one observation.
\end{defn}

From the work above, we will quickly arrive at the following.

\begin{thm}
An experimentally distinguishable set $X$ together with its collection $\mathsf{T}$ of experimental identifications (realized as subsets of $X$) forms a Hausdorff, second-countable topology with open sets given by the verifiable sets. 
\end{thm}
\begin{proof}
It is immediate that the trivial and null observations may be written as experimental identifications, and that they give $X\in\mathsf{T}$ and $\emptyset\in\mathsf{T}$. Proposition \ref{setbehavior} shows that the collection $\mathsf{T}$ is closed under finite intersection and countable union. Because $\mathsf{T}$ is given by an experimental domain of observations, there is a countable basis, so it is second-countable. To show it is closed under arbitrary union, notice that an arbitrary union may be rewritten as a union of basis elements, which is then a countable union, and so it remains in $\mathsf{T}$.
\end{proof}

\begin{cor}
The collection of refutable sets for $X$ is precisely the closed sets for the topology $\mathsf{T}$.
\end{cor}
\begin{proof}
This is immediate from Lemma \ref{complements}.
\end{proof}

And so we have found that all experimentally distinguishable spaces may be given by Hausdorff, second-countable topological spaces. We end this section with an elementary result which has interesting consequences on the theory of experimentally distinguishable spaces.

\begin{prop}
	A Hausdorff and second countable space $X$ has at most the cardinality of the continuum.
\end{prop}

@@

This means that, no matter what technique we use now or in the future, the collections of elements that we can properly define experimentally are at most the cardinality of the continuum. This already gives us a first simple and basic requirement a set of mathematical objects need to pass to be of scientific interest.

@@

@@

Now that we have defined the possibilities of our domains and the topology associated with them, we want to establish relationships between them. We want to do this because the aim of scientific investigation is studying and characterizing these relationships.

@@

\begin{cor}
The topology $\mathsf{T}(\mathcal{C})$ on the set of continuous functions $C(\mathbb{R},\mathbb{R})$ from $\mathbb{R}$ to itself is in general not equal to the open-open topology on $C(\mathbb{R},\mathbb{R})$.
\end{cor}
\begin{proof}
In the proof of the previous proposition, note that the basis for the open-open topology is independent of the basis used for the underlying spaces, and in particular is a superset of the basis for $\mathsf{T}(\mathcal{C})$ when using $\mathbb{B}_2$ to construct it. Hence the open-open topology is distinct from $\mathsf{T}(\mathcal{C})$ when using the basis $\mathcal{B}_1$ on $\mathbb{R}$. 
\end{proof}

@@

\section*{Acknowledgments}
Funding for this work was provided in part by the MCubed program of the University of Michigan. The third author is supported by the National Science Foundation Graduate Research Fellowship Program under Grant No. DGE\#1256260. Any opinions, findings, and conclusions or recommendations expressed in this material are those of the author(s) and do not necessarily reflect the views of the National Science Foundation.
